Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/algorithms.tex
fix typos

First recall \Cref{lem:vector-intersect}, which states that intersection of
indexing schemes is still an indexing scheme. When combined with
\Cref{lem:interval-identities}, we can extend this closure to interval schemes.
Subscripts schemes do not enjoy the same propery as intersection of two
singleton sets might easily be empty, which disqualifies it from being a
subscript index. In the following sections we will not rely on intersection of
subscript indices, so that is not a problem.

>>>>

First recall \Cref{lem:vector-intersect}, which states that intersection of
indexing schemes is still an indexing scheme. When combined with
\Cref{lem:interval-identities}, we can extend this closure to interval schemes.
Subscripts schemes do not enjoy the same property as intersection of two
singleton sets might easily be empty, which disqualifies it from being a
subscript index. In the following sections we will not rely on intersection of
subscript indices, so that is not a problem.
